---
title: "Lab 00 - Hello IDS!"
author: "Alex Walker"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Ross", "Roderick", "Mark", 
           "Andrew", "Alex"),
  github_username = c("Ross-shinnie", "RoderickGAM", "MarkFlorov", 
                      "andrewsusinggithub", "AlexWalker09"), 
  colour = c("powderblue", "thistle", "navy", 
             "red", "orange"),
  hobby = c("Rugby", "running", "football", 
            "climbing", "saxophone"),
  favourite_number = c(2, 7, 4, 5, 4)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The bar chart shows the group members' GitHub username, as well as their favourite colour and number.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "GitHub Username", 
          y = "Favourite Number",
          title = "Group Members")
```

Changed the axes labels and the title.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*Remove this text (including the stars) and add your answer for Exercise 20 here.*
